Comparing Parallel Sorting Algorithms on a High Performance Computing Cluster Using OpenMP

### 2020-11-16 paper/Paper.tex
fixed dupes

    In particular, Quicksort is perhaps the most parallelizable sorting algorithm, and can achieve a linear speedup with few modifications. \cite{blelloch_programming_1996}
    This is because each subarray can be sorted independently, and this leads to speedup. 
    % TODO @Jason add detail on your implementation
    \section{Methodology}
    In this study, the OpenMP \cite{openmp08} API is used for parallization. 
    It is an example of a fork-join methodology	, where each parallel thread forks off from a main thread, then, the results are joined back together. 
    This is implemented into the C programming language via \textit{\#pragma} preprocessor directives. 
    OpenMP is useful for obviously parallel cases, such as Mergesort and Quicksort, as the division of work is quite clear. 
    % TODO add more OMP detail here.

    This work utilizes Case Western Reserve University's Markov cluster, which runs on Intel Xeon x86\_64 Processors. 
    Using the Simple Linux Utility for Resource Management \cite{yoo_slurm_2003} (SLURM), resources are allocated in batch mode, which enables repeatable, large scale experiments with the requested resources. 
    % TODO do we need more detail?

    %sections should always be mergesort -> quick -> heap -> (shell)

>>>>

    In particular, Quicksort is perhaps the most parallelizable sorting algorithm, and can achieve a linear speedup with few modifications. \cite{blelloch_programming_1996}
    This is because each subarray can be sorted independently, and this leads to speedup. 
    %sections should always be mergesort -> quick -> heap -> (shell)
